Graph Data Generators in the World of Big Data

### 2018-05-16 introduction.tex
differences with prior surveys - cont'd

\paragraph*{Contributions} In this survey we will focus on graph data generators in the context of Big Data and related applications of graph algorithms. The key contributions are as follows:

\begin{itemize}
  \item ...
\end{itemize}

@@

>>>>

\paragraph*{Contributions} In this survey we will focus on graph data generators in the context of Big Data and related applications of graph algorithms. The key contributions are as follows:
\begin{itemize}
  \item ...
\end{itemize}

@@

\paragraph*{Differences with prior surveys}

To the best of our knowledge, our work is the first surveying the wide
landscale of graph data generators spanning different Big Data applications and 
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IOT, Telecommunication and graph streaming generators, 
and Machine Learning and Graph Mining generators .

A subset of the graph database
generators, parallel and distributed graph processing generators, along
with a subset of the Semantic Web data generators have been discussed in
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language; along with the
distinguished chokepoints. However, the provided classification is
inherently data-driven and not meant to serve the purpose of letting any
researcher or practitioner interested in Big Data be able to choose a
generator based on its functional features, such as the application domain,
the supported operations and the key configuration options. 
Moreover, our work is much broader and targets different communities, beyond database
and graph processing communities.

\TODO{Outreach other surveys in other communities.}
